EDLD 651 Final Paper

### 2023-12-06 scripts/manuscript.qmd
Fixed figure width so titles didn't cut off

```{r}
#| label: scatterplot

@@

```{r}
#| label: boxplot-gender-ppis-1-score

@@

```{r}
#| label: boxplot-gender-ppis-2-score
ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender",
       tag = "Figure 3.") +
  theme_minimal()

@@

```{r}
#| label: boxplot-gender-ppis-total

@@

```{r}
#| label: boxplot-gender-ss-score
ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender",
       tag = "Figure 5.") +
  theme_minimal()

>>>>

```{r}
#| label: scatterplot
#| fig-width: 7

@@

```{r}
#| label: boxplot-gender-ppis-1-score
#| fig-width: 7

@@

```{r}
#| label: boxplot-gender-ppis-2-score
#| fig-width: 7
ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
  geom_boxplot() +
  theme(legend.position = "none") +
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  labs(x = "Gender",
       y = "Student Defensive Behaviors Score",
       title = "Boxplot of Student Defensive Behaviors Score by Gender",
       tag = "Figure 3.") +
  theme_minimal()

@@

```{r}
#| label: boxplot-gender-ppis-total
#| fig-width: 7

@@

```{r}
#| label: boxplot-gender-ss-score
#| fig-width: 7
ggplot(communication, aes(gender, ss_score, fill=gender)) +
  geom_boxplot() + 
  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
  theme(legend.position="none") +
  labs(x = "Gender",
       y = "Suspicion Scale Score",
       title = "Boxplot of Suspicion Scale Score by Gender",
       tag = "Figure 5.") +
  theme_minimal()
